---
title: "hw0"
author: "Jingyun"
format: html
editor: visual
---

# Exercise

-   For homework 0 you will write a Quarto document that generates an html with the solutions to $f(x) = ax^2+bx+c=0$ for $a = 1, b = 3, c = 2$. Do not report complex solutions, only real numbers. The report should include a plot confirming the result. The html report should not show the code, but the code must be in the Quarto document. The document should include explanations of what the reader is seeing but should be no longer than 1 page.

# Find Solutions

-   To solve a quadratic equation, we need to consider three cases: 

If $b^2-4ac < 0$, then there is no solution to the equation.

If $b^2-4ac = 0$, then there is one solution to the equation.

If $b^2-4ac > 0$, then there are two solutions to the equation.

Then, we apply the formula $$x = \frac{-b \pm \sqrt{b^2-4ac}}{2a}$$ given that $b^2-4ac \geq 0$.

-   We will write a function `solveQuadratic()` to determine whether the quadratic function is solvable, how many solutions there are, and present the solution. 

- Applying the particular $a,b,c$ presented in the exercise, we have

```{r}
#| echo: false
solveQuadratic <- function(a,b,c){
  print(paste0("Your equation is f(x) = ", a,"x^2+",b, "x +", c, "= 0")) # inform the equation
  delta <- (b^2) - (4*a*c) #calculate the value
  
  # The case when there is no solutions
  if (delta < 0){ 
    return (paste0("This function has no solution in real numbers."))
  }
  
  # The case when there are two solutions
  else if (delta > 0){
    xpos <- (-b + sqrt(delta))/(2*a)
    xneg <- (-b - sqrt(delta))/(2*a)
    print(paste0("There are two solutions to your equation. They are ", xpos, " and ", xneg, "."))
  }
  
  #The case when there is only one solution
  else {
    xone <- (-b)/(2*a)
    print(paste0("There is only one solution to your equation. It is", xone))
  }
}

#Where you can change the value of a, b, c
a <- 1
b <- 3
c <- 2
solveQuadratic(a, b, c) #run the function that solves quadratic function
```

## Visual Representation

- Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.

```{r}
#| echo: false
x <- seq(-5,5,length = 300)
plot(x, a*x^2 +b*x + c, type = "l")
abline(h = 0, lty = 2)
```

