---
title: "HW0"
author: "Jingyun"
format: html
editor: visual
---

## Exercises

-   For homework 0 you will write a Quarto document that generates an html with the solutions to $f(x) = ax^2+bx+c=0$ for $a = 1, b = 3, c = 2$. Do not report complex solutions, only real numbers. The report should include a plot confirming the result. The html report should not show the code, but the code must be in the Quarto document. The document should include explanations of what the reader is seeing but should be no longer than 1 page.

```{r}
#| echo: false
solveQuadratic <- function(a,b,c){
  print(paste0("Your equation is ", a,"x^2+",b, "x +", c))
  delta <- (b^2) - (4*a*c)
  if (delta < 0){
    return (paste0("This function has no solution in real numbers."))
  }
  else if (delta > 0){
    xpos <- (-b + sqrt(delta))/(2*a)
    xneg <- (-b - sqrt(delta))/(2*a)
    print(paste0("There are two solutions to your equation. They are ", xpos, " and ", xneg, "."))
  }
  else {
    xone <- (-b)/(2*a)
    print(paste0("There is only one solution to your equation. It is", xone))
  }
}

a <- 3
b <- 7
c <- 2.5
solveQuadratic(a, b, c)
```

-   Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.

```{r}
#| echo: false
x <- seq(-5,5,length = 300)
plot(x, a*x^2 +b*x + c, type = "l")
abline(h = 0, lty = 2)
```

-   Generate a PDF report using knitr. Do not show the R code, only the solutions and explanations of what the reader is seeing.

-   Erase the PDF report and reproduce it but this time using $a=1, b=2, c=5$.

-   Erase the PDF report and reproduce it but this time using $a=1, b=3, c=2$.

-   Create an HTML page with the results for this last set of values, but this time showing the code.
